Trends of SDR in Thessaloniki 

### 2022-10-05 Article.Rmd
Commit 2022-10-05 15:07

documentclass:  article
classoption:    a4paper,oneside
fontsize:       10pt
geometry:       "left=0.5in,right=0.5in,top=0.5in,bottom=0.5in"
link-citations: yes
colorlinks:     yes
urlcolor:        blue

@@

....... span

...... measuremetns CHP1 CM21

....... screening

....... Quality assurance [cite]

Data quality for radiation measurements as described by
CN Long and Y Shi, September 2006, DOE/SC-ARM/TR-074.
Quality Control Procedures/The QCRad Value Added Product Surface
Radiation Measurement Quality Control Testing Including Climatology_Long2006.pdf"

## Data preperation

Due to the large measurement assertenty near the horizon we exclude all measurements
with greater than SZA $85^\circ$. Moreover, due to nearby hills and buildings
we remove data with azimuth angle between $35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$.

## Agregation

>>>>

documentclass:  article
classoption:    a4paper,oneside
fontsize:       12pt
geometry:       "left=0.5in,right=0.5in,top=0.5in,bottom=0.5in"
link-citations: yes
colorlinks:     yes
urlcolor:        blue

@@

<!-- time span -->
Time span for CM21 is 1993-2022 and 2016-2022 for CHP1.

...... Measurements CHP1 CM21

<!-- screening -->
All measurements have been manually screened for inconsistencies and obviously 
problematic data have been excluded.
<!-- physical quantities -->
The conversions to irradiance was done using the calibration factor  .......chp1.... cmp21......
, and adjusting for the dark signal offset daily, using the nights before and after each day.
<!-- Quality assurance -->
A radiation data quality assurance procedure was applied adjusted for the site,
based on methods of Long and Shi [-@long_automated_2008; -@Long2006].
<!-- Data preparation -->
Due to the large measurement uncertainty near the horizon we exclude all measurements
with SZA greater than $85^\circ$. Moreover, due to nearby hills and buildings
we remove data with azimuth angle between $35^\circ$ and $120^\circ$ and SZA greater than $80^\circ$.

![this is a caption](images/longtermtrendsALL-2.pdf)

## Aggregation
